SVG: The Paper

### 2022-04-19 Analysis/index.Rmd
a new colour and some typos

# some more colours
col3 = c("#d7aca1", "#ddc000","#34b6c6",  "#79ad41", "#4063a3")

@@

```{r, fig.cap = "(*left*) The average weight assigned to each selected target by our model. (*right*) The proportion of trials the item with the largest assigned weight as selected by the participant.  Each dot shows data from an individual particpant in a condition and the shaded region indicates the interval in which we expect 67% of participants to fall."}

@@

Is our model calibrated? By this we mean, if our model assigns an item a probability $p$ of being selected next, then is it actually be selected (by the human participant) this often?

@@

We can see from the Figure below that our model is well-calibrated, (at least in terms of the target with the highest assigned weight).

We can also repeat this calculate for the 2nd and 3rd ranked candidate items.

@@

```{r fig.height=3.5, fig.cap = "Histogram of how predictiable indivuidual trials are, defined as how often the model assigned the largest weight to the target that was then selected."}
ggplot(a_trl, aes(prop_max)) + 
  geom_histogram(fill = "#34b6c6", breaks = seq(0, 1, 0.025)) +
  scale_x_continuous("trial predictability")
```

@@

It looks like some of the target selections that our model fails to capture are when participants select a further away target in order to mimimise overall path length. Here we will compare our model's predicted path length against the empirical paths.

>>>>

# some more colours
col3 = c("#d04e00", "#ddc000","#34b6c6",  "#79ad41", "#4063a3")

@@

```{r, fig.cap = "(*left*) The average weight assigned to each selected target by our model. (*right*) The proportion of trials the item with the largest assigned weight was selected by the participant.  Each dot shows data from an individual particpant in a condition and the shaded region indicates the interval in which we expect 67% of participants to fall."}

@@

Is our model calibrated? By this we mean, if our model assigns an item a probability $p$ of being selected next, then is it actually selected (by the human participant) this often?

@@

We can see from the Figure below that our model is well-calibrated (at least in terms of the target with the highest assigned weight).

We can also repeat this calculation for the 2nd and 3rd ranked candidate items.

@@

```{r fig.height=3.5, fig.cap = "Histogram of how predictiable individual trials are, defined as how often the model assigned the largest weight to the target that was then selected."}
ggplot(a_trl, aes(prop_max)) + 
  geom_histogram(fill = "#34b6c6", breaks = seq(0, 1, 0.025)) +
  scale_x_continuous("trial predictability")
```

@@

It looks like some of the target selections that our model fails to capture are when participants select a further away target in order to minimise overall path length. Here we will compare our model's predicted path length against the empirical paths.
